%-------------------------
% Resume in Latex
% Author : Uday Manchanda
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Uday Manchanda} & Email : {uday.manchanda14@gmail.com}\\
  {https://umanchanda.github.io} & Mobile : 908-723-7481 \\
  {https://linkedin.com.com/in/umanchanda} & {https://github.com/umanchanda}
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {New Jersey Institute of Technology (NJIT)}{Newark, NJ}
      {Bachelor of Science in Computer Science;  GPA: 3.46/4.00}{May 2016 -- May 2019 (In progress)}
    \resumeSubheading
      {Case Western Reserve University}{Cleveland, Ohio}
      {Major: Computer Engineering}{Aug 2014 -- May 2016 (Transferred)}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {CircleBlack Inc.}{Newark, NJ}
      {Project Manager Intern: Market Data Feed Automation}{Feb 2019 - May 2019}
      \resumeItemListStart
        \resumeItem{Responsibilities}
          {Led a team of fellow undergraduate students. Project consisted of Python scripts to parse and collect data from Xignite API. Inserted data into MySQL database hosted on AWS based on specific rules.}
      \resumeItemListEnd

    \resumeSubheading
      {Chicago Mercantile Exchange (CME Group)}{New York, NY}
      {Cyber Security Intern}{Summers 2017 and 2018}
      \resumeItemListStart
        \resumeItem{Responsibilities}
          {Assisted in maintaining standard operations procedures and documentation. Provided operational support and responded to inquiries on products such as Riverbed, Guardium, and ArcSight. }
      \resumeItemListEnd

    \resumeSubheading
      {Interpublic Group (IPG)}{New York, NY}
      {Network Security Intern}{May 2016 - December 2016}
      \resumeItemListStart
        \resumeItem{Responsibilities}
        {Implemented Splunk based network intrusion detection system to collect and analyze data from fifty hosts. Assisted in configuring security to enable: data source aggregation, event correlation, and ongoing monitoring. Analyzed alerts reported in Splunk and fine-tuning alert parameters. Conducted Nessus vulnerability scans on email servers to check for vulnerabilities}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Language Interpreter}{Fall 2017}
        {https://github.com/umanchanda/language-interpreter}{Language: C++}
        \resumeItemListStart
            \resumeItem{Specification}
            {Performs lexical, syntactic, and semantic analysis while referencing a symbol table from an EBNF grammar and set of semantic rules}
        \resumeItemListEnd
    \resumeSubheading
        {Web Server}{Spring 2018}
        {https://github.com/umanchanda/webserver}{Language: C}
        \resumeItemListStart
            \resumeItem{Specification}
            {Implemented a simple HTTP server from scratch and responds to page requests from a web browser. Serves HTML pages stored locally. }
        \resumeItemListEnd
    \resumeSubheading
        {Book Review Web Application}{Winter 2019}
        {https://umanchandabooks.herokuapp.com}{Technologies: Flask, PostgreSQL, Jinja2}
        \resumeItemListStart
            \resumeItem{Specification}{Allows user to create and submit a review for a particular novel. User registration and authentication included. API information scraped from Goodreads using requests library. }
        \resumeItemListEnd
    \resumeSubheading
        {Web Authentication Application}{Spring 2019}
        {https://github.com/umanchanda/authentication}{Technologies: React.js, Redux.js, Node.js, Express.js, MongoDB}
        \resumeItemListStart
            \resumeItem{Specification}{Minimal Javascript Full Stack Web Application with user authentication via passport and JWTs}
        \resumeItemListEnd
    \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Languages}{Python, Java, C, SQL, Javascript, C++, LaTeX, R, HTML, CSS}
    \resumeSubItem{Web Development Technologies}{Flask, Django, React.js, Redux.js, Node.js, Express.js, Gatsby.js, jQuery}
    \resumeSubItem{Databases}{SQLite3, MySQL, PostgreSQL, MongoDB, Microsoft SQL Server, GraphQL, Oracle SQL Server}
    \resumeSubItem{Cloud Computing}{Heroku, AWS}
    \resumeSubItem{Coursework}{Advanced Data Structures and Algorithms, Programming Language Concepts, Fundamentals of Network Security, Advanced Programming in Linux, Statistical Methods in Data Science}
  \resumeSubHeadingListEnd
%-------------------------------------------

\section{Awards}
	\resumeSubHeadingListStart
		\resumeSubItem{Eagle Scout Award}{Earned in April 2014 after successfully completing Eagle Project}
	\resumeSubHeadingListEnd
\end{document}
