%-------------------------
% Resume in Latex
% Author : Uday Manchanda
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{amsmath}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item {
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\projectItem}[1]{
	\item {
		\text{#1}
	}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Uday Manchanda} & Email : {uday.manchanda14@gmail.com}\\
  {https://github.com/umanchanda} & Mobile : 908-723-7481 \\
  {https://linkedin.com/in/umanchanda} & {}
\end{tabular*}


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Capital One}{Richmond, VA}
      {Software Engineer}{August 2019 - Present}
      	\resumeItemListStart
	      	\resumeItem{Data Engineering}{March 2021 - Present}
	      	\begin{itemize}
	      		\item Migrated several ETLs from a custom solution to AWS Batch. Set up necessary infrastructure to run the jobs on a daily cadence, while also setting up alerting for failures. 
	      		\item Helped reduce costs and improve developer experience by utilizing a single dashboard for verifying the status of these ETLs
	      		\item Reduced costs by streamlining Snowflake queries into a single AWS Lambda function and published to an internal streaming platform. 
	      		\item Increased flexibility of existing API by allowing for a more permissive schema when collecting data from MongoDB and then published to a Snowflake DB. 
	      	\end{itemize}
      		\resumeItem{Site Reliability Engineering}{August 2019 - March 2021}
      		\begin{itemize}
      			\item Created CI/CD pipeline in Jenkins to enable hands-off deployments from Development to Production. 
      			\item Enabled developers to identify code quality issues earlier through CI checks. 
      			\item Enhanced capabilities of existing custom-built failover/failback tool by increasing code coverage and adding new features. Onboarded users to this tool.
      		\end{itemize}
        \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubheading
        {NBA-API}{Technologies: Golang, Docker}
        {https://github.com/umanchanda/NBA-API}{}
        \resumeItemListStart
            \projectItem{A simple API that scrapes data from Basketball Reference}
            \projectItem{Provides information about games, scores, and other various statistics.}
        \resumeItemListEnd
    \resumeSubheading
    	{Phonebook Application}{Technologies: React.js, Node.js, Express.js, MongoDB}
    	{https://github.com/umanchanda/phonebook-application}{}
	    \resumeItemListStart
	    	\projectItem{Full Stack Application that performs CRUD operations for a simple phonebook. }
	    \resumeItemListEnd
    \resumeSubheading
        {Finance Application}{Technologies: Flask, SQLite3, Docker}
        {https://github.com/umanchanda/umanchandastocks}{}
        \resumeItemListStart
            \projectItem{Simple Web Application that performs stock trading capabilities.}
        \resumeItemListEnd
    \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Languages}{Python, Node.js, Golang}
    \resumeSubItem{Cloud Computing}{AWS}
    \resumeSubItem{Web Development}{React.js, Flask}
    \resumeSubItem{CI/CD}{Jenkins, Heroku}
    \resumeSubItem{Misc}{Git, Docker, Terraform}
    \resumeSubItem{Databases}{Snowflake, MongoDB, PostgreSQL}
  \resumeSubHeadingListEnd
%-------------------------------------------

%-----------EDUCATION-----------------
\section{Education}
	\resumeSubHeadingListStart
		\resumeSubheading
		{New Jersey Institute of Technology (NJIT)}{Newark, NJ}
		{Bachelor of Science in Computer Science;  GPA: 3.43/4.00}{Graduated: May 2019}
	\resumeSubHeadingListEnd

\section{Certifications}
	\resumeSubHeadingListStart
		\resumeSubItem{AWS Certified Solutions Architect Associate}{Received: September 2021}
	\resumeSubHeadingListEnd
\end{document}
